Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-12-22 RR_manuscript/Draft_RR.tex
fix typos, expand parts of methods; up to Step 4

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
In these studies the datasets were fixed and data collection or measurement could not be changed.

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.

@@

One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e.~how to operationalize it.
Take for example the following sentence: ``Sheila says Pat is clever.''
Now, imagine we are interested in measuring the difference between that sentence and the sentence ``Sheila says \emph{Mat} is clever.''
How can we obtain a measure of dissimilarity between the first sound in \emph{Pat} and the first sound in \emph{Mat}?
If we want to compare ``Sheila says PAT is clever'' to ``Sheila says Pat is CLEVER,'' how do we quantify the difference between the two utterances?
What if we are interested in how the argumentative nature of ``Sheila says Pat is clever'' and the expression of surprise in ``Sheila says Pat is clever?!'' are conveyed in speech?
How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
The acoustic signatures of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
The initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
Studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.

When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~``a blue banana'' vs.~``a yellow banana'')?
We are interested in the acoustic profile of referring expression.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective ``yellow'' to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
Even looking at morphosyntactically identical expressions, speakers can modulate these expressions via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on `banana' to indicate the contrastive nature of the \emph{noun}.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on `yellow' to indicate the contrastive nature of the \emph{modifier}. In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

INFORMATION ABOUT THE DATA SET AND EXP DESIGN

@@

The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results. We are further interested in which factors affect researchers' final results.

@@

We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection. The analysis will substantially diverge from their approach (see §\#.\#)

This project involves a series of steps (X-X):
First, we recruit independent groups of researchers to analyze the data.
Second, We give researchers access to the speech corpus and let them analyze the data as they see fit.
Third, we generate peer review ratings of the analyses (based on methods, not results).
Forth, we evaluate the variation among the different analyses.
And finally, we collaboratively produce the final manuscript.
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

@@

Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as `analysis teams.'

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
All analysts will sign a consent (ethics) document (LINK).

We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity (\(\tau^2\)) with a 95\% confidence interval that does not encompass zero.
This minimum sample size is invariant regardless of \(\tau^2\).
This is because the same t-statistic value will be obtained by the same sample size regardless of variance (\(\tau^2\)).
We see this by first examining the formula for the standard error, SE for variance, (\(\tau^2\)) or SE(\(\tau^2\)) assuming normality in an underlying distribution of effect sizes (Knight 2000):

@@

and then rearranging the above formula to show how the t-statistic is independent of \(\tau^2\), as seen below.

\[t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}\]

We then find a minimum n = 12 according to this formula.

@@

Analysis teams will register and answer a demographic and expertise survey (LINK). The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
We will then provide teams with the acoustic data set and request that they answer the following research question:

@@

Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

``Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{99}
  \tightlist
  \item
    A perfect analysis with no conceivable improvements from the reviewer.
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{74}
  \tightlist
  \item
    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{49}
  \tightlist
  \item
    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{24}
  \tightlist
  \item
    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{-1}
  \tightlist
  \item
    A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
  \end{enumerate}
\end{itemize}

@@

After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:

\noindent ``Please explain your ratings of this analysis.
\noindent Please evaluate the selection of acoustic features.
\noindent Please evaluate the measurement of acoustic features.
\noindent Please evaluate the choice of statistical analysis type.
\noindent Please evaluate the process of choosing variables for and structuring the statistical model.
\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
\noindent Please evaluate the suitability of the structure of the statistical model.
\noindent Please evaluate choices to exclude or not exclude subsets of the data.
\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''

After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''

>>>>

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

@@

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
In these studies the data sets were fixed and data collection or measurement could not be changed.

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
\textless\textless\textless\textless\textless\textless\textless{} HEAD
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
=======
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{} 4860d0ed0c2fc204883e1c150efb5749b4ef1669

@@

Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:

``I hope Liz does not go to the grocery store tomorrow.''

Depending on the speaker's intention, this sentence can be said in different ways.
If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow.
If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.

If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.

Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
The acoustic signatures of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
The initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).

When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.). Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
The present paper probes this garden of forking path in speech analysis. To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations? (e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
We are interested in the acoustic profile of referring expressions.
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.

Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

@@

The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
We are further interested in which factors affect the researchers' final results.

@@

We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection.
However, the analysis will substantially diverge from their approach (see §\#.\#)

This project involves a series of steps (X-X):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  We will recruit independent groups of researchers to analyze the data.
\item
  We will give researchers access to the speech corpus and let them analyze the data as they see fit.
\item
  We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
\item
  We will evaluate the variation among the different analyses.
\item
  Lastly, we will collaboratively produce the final manuscript.
\end{enumerate}

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

@@

The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
All analysts will sign a consent (ethics) document (LINK).

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity (\(\tau^2\)) of the effect sizes reported by the analysis teams.
Ideally, the 95\% credible interval of \(\tau^2\) should not include 0 (i.e.~we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a \emph{t}-statistic that would correspond to a \emph{p}-value smaller than 0.05).
Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that \emph{t} will be the same regardless of \(\tau^2\):

\[t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}\]

In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
When \(n = 12\) then \(t_{12-1} = t_{11} = 2.3452\) and \(p = 0.0388\).
A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.

@@

The analysis teams will register and answer a demographic and expertise survey (LINK).
The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
We will then provide teams with the acoustic data set and request that they answer the following research question:

@@

Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{99}
  \tightlist
  \item
    A perfect analysis with no conceivable improvements from the reviewer.
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{74}
  \tightlist
  \item
    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{49}
  \tightlist
  \item
    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{24}
  \tightlist
  \item
    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{-1}
  \tightlist
  \item
    A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
  \end{enumerate}
\end{itemize}

@@

After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:

\noindent ``Please explain your ratings of this analysis.
\noindent Please evaluate the selection of acoustic features.
\noindent Please evaluate the measurement of acoustic features.
\noindent Please evaluate the choice of statistical analysis type.
\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
\noindent Please evaluate the suitability of the structure of the statistical model.
\noindent Please evaluate choices to exclude or not exclude subsets of the data.
\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''

After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''
